Capstone Movielens Report

### 2025-12-13 reports/capstone-movielens.site/05.appendix.Rmd
Function described: `calc_UMGY_SmoothedDay_effect.RMSE.cv`.

>>>>

Validates the *UMGYD Effect (UMGYDE) Model* represented by the data object passed in the [day_smoothed_effect](#func.calc_UMGY_SmoothedDay_effect.RMSE.cv.args.day_smoothed_effect) argument with use of *K-Fold Cross-Validation* as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV].

::: {.noteblock data-latex=""}
The $K$ value for the *K-Fold Cross-Validation* is determined by the length of the [`edx_CV` Object] (in *this Project* we use $K = 5$).
:::

```{r eval=FALSE}
lss.UMGYD_effect.RMSE <- calc_UMGY_SmoothedDay_effect.RMSE.cv(lss.UMGYD_effect)
```
:::

::: { #func.calc_UMGY_SmoothedDay_effect.RMSE.cv.args.day_smoothed_effect .sidebar }
  - **day_smoothed_effect:** Dataframe object representing the *UMGYDE Model*.

This function commits the *UMGYDE Model* validation by calculating the *Root Mean Squared Error (RMSE)* on the validation datasets contained in the [`edx_CV` Object] described below in [Appendix B: Models Training Datasets].

::: {.noteblock data-latex=""}
This function internally calls the [calc_UMGY_SmoothedDay_effect.MSE.cv](#func.calc_UMGY_SmoothedDay_effect.MSE.cv) auxiliary function described above in *this Section* to compute the *MSE* for the *UMGYDE Model* and then calculates the *square root* of the obtained result.
:::

In *this Project*, the *UMGYDE* data object representing the *UMGYDE Model* (and being passed in the [day_smoothed_effect](#func.calc_UMGY_SmoothedDay_effect.RMSE.cv.args.day_smoothed_effect) argument) is created and returned by the following functions described above in *this Section*:

::: {.noteblock data-latex=""}
This function is also called internally as an auxiliary function from the [train_UMGY_SmoothedDay_effect.RMSE.cv](#func.train_UMGY_SmoothedDay_effect.RMSE.cv) and [regularize.test_lambda.UMGYD_effect.cv](#func.regularize.test_lambda.UMGYD_effect.cv) functions described below in sections [UMGYDE Model: Tuning `loess` Params] and [UMGYDE Model: Regularization], respectively, of *this Appendix*.
:::
:::

The source code of the [calc_UMGY_SmoothedDay_effect.RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L169) function is shown below:
```{r eval=FALSE}
calc_UMGY_SmoothedDay_effect.RMSE.cv <- function(day_smoothed_effect){
  sqrt(calc_UMGY_SmoothedDay_effect.MSE.cv(day_smoothed_effect))
}
```
